\sysfull

### 2018-04-15 paper/evaluation.tex

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/overallOverhead}
	\caption{ overall overhead breakdown: nc: No Coalecing, sc: Slow Coalescing, ea: Energy Aware coalescing \todo{}{Przemek}}
	\label{fig:overallOverheadBreakdown}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalEfficiency}
	\caption{ Coalescing algorithm efficiency:  nc: No Coalecing, sc: Slow Coalescing, ea: Energy Aware coalescing, eat: Energy \& Task Aware coalescing \todo{}{Przemek}}
	\label{fig:coalEfficiency}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/memAccess}
	\caption{ Memory access overhead breakdown:  nc: No Coalecing, sc: Slow Coalescing, ea: Energy Aware coalescing \todo{}{Przemek}}
	\label{fig:coalEfficiency}
\end{figure}

@@

>>>>

@@

\indent \textbf{Overall \sys Overhead Breakdown.} The result is presented in Figure~\ref{fig:overallOverheadBreakdown}.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/overallOverhead}
	\caption{Overall \sys overhead breakdown; nc: no coalescing, sc: slow coalescing, ea: energy-aware coalescing.}
	\label{fig:overallOverheadBreakdown}
\end{figure}

\textbf{\sys Coalescing Algorithm Efficiency.} The result is presented in Figure~\ref{fig:coalEfficiency}.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalEfficiency}
	\caption{\sys coalescing algorithm efficiency; nc: no coalescing, sc: slow coalescing, ea: energy-aware coalescing, eta: energy and task-aware coalescing.}
	\label{fig:coalEfficiency}
\end{figure}

\textbf{\sys Memory Access Overhead Breakdown.} The result is presented in Figure~\ref{fig:coalmemory}.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/memAccess}
	\caption{\sys memory access overhead breakdown; nc: no coalescing, sc: slow coalescing, ea: energy-aware coalescing.}
	\label{fig:coalmemory}
\end{figure}

### 2018-04-15 paper/hwswsetup.tex

We evaluated \sys in two power supply environments: (i)  \emph{intermittent} and (ii) \emph{fixed} (to benchmark the intermittent power supply results). In the experiments with intermittent power supply, we evaluated \sys using a WISP\,5.1~\cite{wisp5,wisp}---energy-harvesting platform build around a MSP430FR5969~\cite{wolverine} MCU with with 64\,kB of non-volatile (FRAM) memory and and 2\,kB of volatile memory (SRAM). MCU was operating at 1\,MHz clock cycle. We powered the WISP using RF signal generator~\cite{} \todo{Add reference to signal generator}{Przemek} emitting 20\,dBm sinusoidal wave at 915\,MHz.  Signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic antenna~\cite{atlas2015}. For distance-controlled experiments, we affixed WISP at two paper protrusions around 10\,cm from the surface of the table (parallel to, and at the edge of, the table surface). Antenna of the signal generator was facing WISP directly and located at three distances, $d=\{15, 30, 50\}$\,cm, from WISP. For the task downscaling experiments, an additional distance of $d=60$\,cm was considered. Both antennas were parallel to each other and no physical objects were located between the WISP and the signal generator antenna. For continuous power experiments we used an alternative setup with MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad}, which had the same MCU as WISP. In all the experiments the timing measurements were performed using either the Saleae~\cite{saleae} logic analyzer (for intermittent power experiments) or TI Code Composer Studio (for fixed power experiments). \todo{provide version and more details on TI CCS}{Przemek} Both type of experiments are explained in the following section.

>>>>

We evaluated \sys in two power supply environments: (i)  \emph{intermittent} and (ii) \emph{fixed} (to benchmark the intermittent power supply results). In the experiments with intermittent power supply, we evaluated \sys using a WISP\,5.1~\cite{wisp5,wisp}---energy-harvesting platform build around a MSP430FR5969~\cite{wolverine} MCU with with 64\,kB of non-volatile (FRAM) memory and and 2\,kB of volatile memory (SRAM). MCU was operating at 1\,MHz clock cycle. We powered the WISP using RF signal generator~\cite{} \todo{Add reference to signal generator}{Przemek} emitting 20\,dBm sinusoidal wave at 915\,MHz.  Signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic antenna~\cite{atlas2015}. For distance-controlled experiments, we affixed WISP at two paper protrusions around 10\,cm from the surface of the table (parallel to, and at the edge of, the table surface). Antenna of the signal generator was facing WISP directly and located at three distances, $d=\{15, 30, 50\}$\,cm, from WISP. For the task downscaling experiments, an additional distance of $d=60$\,cm was considered. Both antennas were parallel to each other and no physical objects were located between the WISP and the signal generator antenna. Every benchmark we used (refer to next section) was run repeatedly for X\,s and the result was averaged for the duration of the experiment. \todo{check if this is correct}{Carlo} For continuous power experiments we used an alternative setup with MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad}, which had the same MCU as WISP. In all the experiments the timing measurements were performed using either the Saleae~\cite{saleae} logic analyzer (for intermittent power experiments) or TI Code Composer Studio (for fixed power experiments). \todo{provide version and more details on TI CCS}{Przemek} Both type of experiments are explained in the following section.
